**Evaluation of machine learning methods for 16S rRNA gene data**

### 2019-03-06 submission/manuscript.Rmd
figures and text changes

We interpreted the feature weights of L1 and L2 SVM with linear kernel and log odds ratios of L2 logistic regression using the training data. To get a sense of the importance of each feature we randomly subsampled 80% of the data 100 times and trained 100 models; this resulted in 100 different sets of feature weights. We reported the mean weights of the 10 most important features for[Figure 4]. FIT levels were

>>>>

We interpreted the feature weights of L1 and L2 SVM with linear kernel and regression coefficients of L2 logistic regression using the training data. To get a sense of the importance of each feature we randomly subsampled 80% of the data 100 times and trained 100 models; this resulted in 100 different sets of feature weights. We reported the mean weights of the 10 most important features [Figure 4]. FIT levels were
